Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
Fix confusion between project and library.

Computability is a key topic in Computer Science teaching. Moreover O'Connor's library is a nice illustration of dependently typed programming, so we chose to devote a full chapter (chapter 9 of~\cite{HydraBook}) to this formalization, with comments on the definitions and proofs, [counter]-examples and exercises, and  extract part of the Goedel library into a new sub-library of the \Hydras library: Ackermann.

>>>>

Computability is a key topic in Computer Science teaching. Moreover O'Connor's library is a nice illustration of dependently typed programming, so we chose to devote a full chapter (chapter 9 of~\cite{HydraBook}) to this formalization, with comments on the definitions and proofs, [counter]-examples and exercises, and  extract part of the Goedel library into a new sub-library of the Hydra-battles library: Ackermann.
